INTELLIGENT SYSTEMS

### 2021-04-07 paper_5.tex
finish 5.4.3

>>>>

\subsubsection{Input data}
A data augumentation process is carried out to increase the amount of data 
available for training. In this way, instead of giving a single sequence S 
as input, three will be given, more precisely:
\begin{itemize}
    \item A Gaussian noise is added to the input signal;
    \item The sequence S is resized with a random value between 0.7 and 1.1;
    \item A sequence of 10 numbers is first interpolated to S and then the resulting sequence is sampled.
\end{itemize}
Each sequence (S) is divided into 100 sub-sequences ($ s_i $) (100Hz = 1 per 
second), a number enough to contain a walk, with overlap equal to 75\%.

\subsubsection{Implementation details}
First 100 epochs are performed in order to train the model, with the training 
set divided into training and validation. At the end of the training, in order to 
be able to fine-tune the parameters, a further 50 epochs are performed with 
the training set only. The optimization is carried out with the stochastic 
gradient descent (SGD) standard with a mini-batch of 128 samples, weigth 
decay of 0.0005 and a moment of 0.9. The total accuracy is obtained by 
combining the accuracies derived from the output of each sub-sequence ($ s_i $) 
of the input S. To obtain this, simply multiply each probability obtained 
from each of the sub-sequences with the following equation:
\begin{equation}
    P(S=c) = \prod_{i=1}^UP_i(s_i=c)
\end{equation}
Where U is the number of subsequences $ s_i $, P(s=c) is the probability of assign the identity \emph{c} to the person in sequence S and $ P_i(s_i=c) $ is the probability of assign the identity \emph{c} to teh person in subsequence $ s_i $.

\subsubsection{Gait Recognition experiments}
\begin{enumerate}
    \item \emph{Sensor position}: 
\end{enumerate}
